Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-11 shanghai.tex
Proof that 10.2 is a homomorphism; still needs isomorphism

  It only remains to show that \eqref{pich1} is a group
  isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two character sheaves.  
  \Clifton{Straightforward, yes, but it still needs to be written down here.}
\end{proof}

>>>>

  It only remains to show that \eqref{pich1} is a group
  isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two character sheaves.
  If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes s'$ is a global section for
  $\cs{L} \otimes \cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes \cs{L}'$ imply that
  $\tau_{\cs{L} \otimes \cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$.

  \Clifton{Straightforward, yes, but it still needs to be written down here.}
\end{proof}
